---
title: "USA Unemployment Graphing By Year"
author: "Kailash Natarajan"
date: "06/07/2020"
output: ioslides_presentation
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
## Description
- This is a presentation explaining my project for Developing Data Products (Week 4).

## Graphing Unemployment

- The project graphs the unemployment count on y-axis and month on x-axis. 
- The year in x-axis is selected by the user using a sliding bar
- It has been implemented using plotly to enhance user experience.

## Code used in ui.R
- Not much complications here
```{r,eval=FALSE,echo=TRUE}
library(shiny)
library(plotly)
shinyUI(fluidPage(
    # Application title
    titlePanel("UNEMPLOYMENT GRAPH FOR USA IN THE YEAR SELECTED"),
    # Sidebar with a slider input for year
    sidebarLayout(sidebarPanel(sliderInput("year",
                        "Select the year:",min = 1967,
                        max = 2015, value = 2000)
        ),
        # Show a plot of the generated graph
        mainPanel(plotlyOutput("plot")
        ))))
```

## Code used in server.R
- Very simple and reproducible, just subsetting data and plotting.
```{r,eval=FALSE,echo=TRUE}
library(shiny)
library(plotly)
library(lubridate)
shinyServer(function(input, output){
output$plot <- renderPlotly({
  data("economics")   # Our data containing dataset
  year_selected<-input$year  #Getting input from user 
  # Subsetting data
  economics<-economics[
    year(economics$date)==year_selected,c("date","unemploy")]   
  #Generate Plot
  myplot<-plot_ly(data=economics,x=~date,y=~unemploy,trace="scatter")    
    myplot<-myplot %>% add_lines(data=economics,y=~unemploy,
                                 color=I("red") )
      myplot  })})
```